% !TeX spellcheck = en_US
\documentclass[11pt,a4paper]{article}


\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphics}
\usepackage{hyperref}
\usepackage{physics}
\usepackage{cite}
\usepackage{todonotes}
\usepackage{comment}
\usepackage{authblk}
\usepackage{optidef}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{booktabs}
\captionsetup{subrefformat=parens}

\title{}
\author[1,2]{Ludmila Botelho}
\author[1]{\"Ozlem Salehi}
\affil[1]{Institute of Theoretical and Applied Informatics, Polish Academy of Sciences, Bałtycka~5, 44-100 Gliwice, Poland}
\affil[2]{Joint Doctoral School, Silesian University of Technology, Akademicka 2a, 44-100 Gliwice, Poland}
\date{}

\begin{document}
	\maketitle
	\begin{abstract}

\end{abstract}


% Goal: 1) Quantum 
%		2) Quantum Information Processing 
%		3) Journal of Discrete Mathematics



% Main idea: Operational Fixed Interval Scheduling Problem with no Idle time


% Introduction: previous work and problem definition (briefly). 
% 
% Qubo formulation: more technical and formal definition

% Experement: Music Reduction

\section{Introduction}

Quantum algorithms caused novelty and excitement with the possibility of speed up and efficiency compared with the classical counterparts. However, the limitation for current devices imposes a new paradigm: the Noisy Intermediate-Scale Quantum (NISQ) computing.

Algorithms that can run on such NISQ devices have been developed, such as Quantum Annealing (QA) and the Quantum Approximate Optimization Algorithm (QAOA) are among the most promising ones \textcolor{red}{[add citations]}. A better understanding of the performances of these approaches on industrial problems is of great interest, both for quantum computing adoption and for the application domains concerned. 

Quantum Annealing is used for solving optimization tasks expressed in term of a Ising Hamniltonian \textcolor{red}{[Should we cite lucas2018? how much should we talk about Ising Model in QUBO section? Should we add something about D-Wave as well?]}, designed in such a way that its ground state encapsulates the optimal solution to the considered problem.

\textcolor{red}{Paragraphy to describe previous applications of QA to unconstrained optimization and scheduling problems} \cite{ikeda2019application}


We demonstrate the use of QA to solve ???? and we evaluate its efficiency and accuracy for this problem
from empirical results. Our approach uses the commercial quantum annealer available from D-Wave Systems to
implement several hard constraints. The D-Wave 2000Q is a commercially available quantum annealing device... By reducing ???? to QUBO form and then embedding this problem into the D-Wave processor, we use QA to reduce a complex music sheet to simpler version, a problem known as Music Arrange Reduction. 

% TODO: change notation for machine and jobs
\section{Interval Scheduling Problem}
\subsection{Problem Definition}
The Fixed Interval Scheduling problem consists of planning a set of $N$ jobs $\{J_1, \cdots,J_N \}$ on a set of $M$ resources or physical machines $\{R_1, ...,R_M \}$. Each $J_i$ job has a  profit $w_j$ and consists of a set of operations $\{V_{i1}, \cdots , V_{iM} \}$ that have to be executed sequentially. The jobs have fixed start and end times and are assigned to at most one machine, which are continuously available. The objective is to select a set of jobs assing them to the machines so as to maximize the profit with minimum idle time. 
\subsection{General form}

This is the approach used to model fixed job scheduling \cite{arkin1987scheduling, barcia2005k}. 

Let $L $ be the number of jobs. Let us denote the set of jobs $ p_1,p_2,\dots,p_L $ by $ P $. Let $ G=(P,E) $ be the graph with vertices $ P $ such that edge $(i,j) \in E$ if jobs $ i $ and $ j $ are compatible i.e. they do not intersect.

Let $ x_{ij} $ be the assignment variable such that
\begin{equation}
x_{ij} =   \begin{cases}%
1,      & \text{if job $i$ is assigned to machine $j$}\\
0, & \text{otherwise.}
\end{cases}
\end{equation}
for $ i = 1, \dots ,L $ and $ j=1, \dots ,M  $. $ e(p_i) $ denotes the weight for job $ p_i $. The goal is to maximize 
\begin{equation}
\sum_{i=1}^L \sum_{j=1}^M e(p_{i})x_{ij}	
\end{equation}
such that
\begin{align}
&\sum_{j=1}^M x_{ij} \leq 1 \mbox{ for }i=1\dots L \\
&\sum_{i \in I} x_{ij} \leq 1 \mbox{ for } I \subseteq P
\end{align}
where $ I $ in any maximal independent set of $ G $.


The first constraint ensures that each job is assigned to at most one machine. The second constraints ensures that incompatible jobs are not selected. In our case, $ G $ is an interval graph and the problem is solvable in time $ O(L^2 \log L) $ by a classical algorithm. The number of variables required by this approach is $ O(LM) $. Note that $ L $ depends on the number of machines and the number of process in the job set.

The drawback of this formulation is that it does not take into consideration if after the optimization some machines are idle in a given time period. It can even be the case that all machines are idle at a time point.  


\subsection{No Idle Time}
% measure = time unity 
% for each job: define start and ending time
% lengh of the song  = max (e_t)

In order to overcome this, we will define the following formulation. Let $ p_{ij} $ denote the $ j $'th phrase of track $ i $. Let us define the binary variable $x_{ij}$ such that:
\begin{equation}
%change to x_j, (job selected or not)
x_{ij} =   \begin{cases}%
1,      & \text{$j$'th phrase of track $i$ is selected}\\
0, & \text{otherwise.}
\end{cases}
\end{equation}
for $ i = 1, \dots ,N $ and $ j=1, \dots ,P_i  $ where $P_i$ is the number of phrases in track $i$.


Assuming that each phrase ends exactly at the end of a measure, we can propose the following binary variables $m_{ik}$ such that
\begin{equation}
m_{ik} =   \begin{cases}%
1,      & \text{Measure $k$ from track $i$ is selected}\\
0, & \text{otherwise.}
\end{cases}
\end{equation}

We have the following relationship between the phrases and measures:

\begin{equation}\label{eq:phrasemeasure}
x_{ij} = 1 \iff m_{ik}=1 \mbox{ for } k \in S_{ij}
\end{equation}
where $S_{ij}$ is the set of measures that the phrase $p_{ij}$ consists of. This can be incorporated by adding the terms 
\begin{equation}
x_{ij}(1-m_{ik})
\end{equation}

The goal is to maximize:
\begin{equation}
\sum_{i=1}^N\sum_{j=1}^{P_i} e(p_{ij})x_{ij}
\end{equation}
such that
\begin{equation}\label{eq:mtrack}
\sum_{i=1}^N m_{ik} = M \mbox{ for }k=1,\dots, K 
\end{equation}
where $K$ is the number of measures in the music piece. 

The constraint defined by Eq.\eqref{eq:mtrack} ensures that $M$ measures are selected among $ N $ at any given time. Note that this is a soft constraint while the constraint defined in Eq. \ref{eq:phrasemeasure} is a hard constraint. The number of variables required by this formulation is upper bounded by $ O(L+NK) $.

Note that the obtained solution does not give us information about which phrase should be assigned to which track. But once we have the assignment to the binary variables $ x_{ij} $, this can be determined using the following classical algorithm:

\section{Quantum Annealing}
The way a problem is solved on this device is to package the problem at hand into a Hamiltonian, employing the quadratic unconstrained binary optimization (QUBO) formalism

Suppose that there are $ N $ tracks in the song and the goal is to reduce the number of tracks to $ M $.

 
 \subsection{More advanced formulation}
 
 Now suppose that we want to add restrictions about the assignment of phrases to particular tracks. In this case, we will slightly modify our formulation which takes the following form.
 
  Let us define the binary variable $x_{ij}^t$ such that:
 \begin{equation}
 x_{ij}^t =   \begin{cases}%
 1,      & \text{$j$'th phrase of track $i$ is assigned to track $ t $}\\
 0, & \text{otherwise.}
 \end{cases}
 \end{equation}
 for $ i = 1, \dots ,L $ and $ j=1, \dots ,P_i  $ and $ t = 1, \dots, M $.
 
\begin{equation}
 x_{ij}^t = 1 \implies m_{ik}=1 \mbox{ for } k \in S_{ij}.
 \end{equation}

 The goal is to maximize:
 \begin{equation}
 \sum_{t=1}^M \sum_{i=1}^L\sum_{j=1}^{P_i} e(p_{ij})x_{ij}^t
 \end{equation}
 such that
 \begin{equation}
 \sum_{i=1}^N m_{ik} = M \mbox{ for }k=1\dots K. 
 \end{equation} 
 We also need to add a constraint so that the same phrase is not selected for multiple tracks:
  \begin{equation}
 \sum_{t=1}^M x_{ij}^t \leq 1 \mbox{ for }i=1\dots L, j=1 \dots P_i. 
 \end{equation}
 
 Suppose that we want to add a restriction about phrases that should not be assigned to a particular track $ t $. For instance we may restrict phrase $ p_{ij} $ following phrase $ p_{i'j'} $ when the interval between the last note of phrase $ p_{ij} $ and the first note of phrase $p_{i'j'} $ is larger than a particular value or an unwanted interval and the last measure of $ p_{ij} $ and the first measure of $ p_{i'j'} $ are consecutive measures. Then we can add the following term to the objective function:
 \begin{equation}
 x_{ij}^tx_{i'j'}^t
 \end{equation} 
 for each $ t=1,\dots,M $.
 
 Furthermore, it can be the case that the certain phrases $ p_{ij} $ should not be assigned to a particular track $ t $. This can be accomplished by adding the following term to the objective:
 \begin{equation}
 (1-x_{ij}^t).
 \end{equation} 
 
 \subsection{Further conditions}
 Suppose that two measures should not be selected at the same time. Such a condition might be desirable when two measures played at the same time might create a dissonance and can be incorporated adding the following term to the objective function
 \begin{equation}
 m_{ik}m_{i'k'}
 \end{equation}  
for any pair of undesirable measures $m_{ik}$ and $ m_{i'k'} $. 

\bibliographystyle{ieeetr}
\bibliography{paper}
\end{document}